Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-28 writeup/gz_hubble_data.tex
Center all the floating images

One of the major difficulties in studying the morphologies of galaxies in large samples lies in the system of measurement. Visual classification by experts has been used for many years \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}. These methods have advantages in using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration. Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts. The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images. With $>2\times10^5$~classifiers, this allows for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible. While the crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

@@

\begin{figure*}
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in Galaxy Zoo: Hubble. The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope which were used to create color gradients in the composite images for COSMOS.\label{fig:filtercurves}}
\end{figure*}

@@

Since the majority of the data in Legacy surveys described in \S\ref{ssec:legacy_surveys} had images in only 1 or 2~bands available when GZH was launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo was not possible. For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band is mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two. Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}. The 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).

@@

\begin{figure*}
\includegraphics[width=160mm]{figures/specz_comparison.pdf}
\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogs. The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel. Within this range there is over 98\% agreement in redshifts between all three catalogs.}
\label{fig:speczs}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
\caption{Flowchart of the questions presented to GZH users, labeled with the corresponding Task numbers. Tasks in the decision tree are color-coded by tier level: Gray-colored Tasks are 1st tier questions which are asked of all users. Tasks colored green, blue, purple, and pink (respectively) are one, two, three, or four steps below branching points in the decision tree.}
\label{fig:decisiontree}
\end{center}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/zeta_examples.pdf}
\caption{Behavior of the normalized, weighted vote fractions of features visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the artifical \ferengi{} images. Galaxies are a random selection of images with $e=0$ and at least three detectable images in redshift bins of $z\ge0.3$. The measured vote fractions (red points) are fit with an exponential function (Equation~\ref{eqn:fzeta}); the best-fit parameters are given above each plot. Error bars are Poissonian, assuming a median of 40~votes per galaxy.}
\label{fig:zeta_examples}
\end{center}
\end{figure*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.50\textwidth]{figures/zeta_mu.pdf}
\caption{All fits for the vote fraction dropoff parameter $\zeta$ for $f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface brightness. This includes only the 37~galaxies with a reasonably bounded range on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit the function.}
\label{fig:zeta_mu}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), uncorrectable (green), and NEI (pink) galaxies in the full GZH sample. The uncorrectable galaxies tend towards higher redshift, slightly lower in surface brightness, and lower values of $p_{features}$ than the correctable galaxies. The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
\label{fig:z_mu_p}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), uncorrectable (middle), and NEI (right) galaxies in the GZH sample.}
\label{fig:debiased_corrections}
\end{center}
\end{figure*}

@@

\subsection{Comparison to other catalogs}\label{ssec:comparisons}

@@

\subsubsection{COSMOS}

The COSMOS galaxies have several published datasets automatically classifying their morphologies, all using a variation of non-parametric measurements clustered with machine algorithms and trained on a visually-classified reference set of several hundred galaxies. \citet{cas07} use a combination of $C$, $A$, $G$, and $M_{20}$ \citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$. They divide galaxies into three broad morphological categories: early-type, spirals, and irregulars. A very similar method is employed by \citet{tas11}; they use the same non-parametric indices to determine galaxy morphology, but with a slightly different method of calculating the Petrosian radius. 64\% of the galaxies have identical classifications in \citet{cas07} and \citet{tas11}; roughly two-thirds of the disagreements are galaxies originally classified as ``irregular'' in \citet{cas07} but ``spiral'' in \citet{tas11}.

Using a 0.5\arcsec{} positional match, we find 76,241 galaxies with morphologies in both GZH and \citet{cas07}. At the lowest values of \pbest, $\sim10\%$ of the \citet{cas07} galaxies are classified as irregular, only $\sim30\%$ as early-type, and $60\%$ as spiral. The early-type fraction drops with increasing \pbest, with an increasing proportion of irregulars. The \podd{} vote fraction distinguishes sharply between spirals and irregulars at \podd$>0.2$.

Despite using a similar classification method to \citet{cas07}, the \citet{tas11} classifications show significantly different trends as a function of GZH classifications. Spiral galaxies consistently make up $\sim60\%$ of the sample at \emph{all} \pbest, with a mild increase at \pbest$\simeq1.0$. Early-type and irregular galaxies make up the remainder, smoothly varying between irregulars at low \pbest{} and early-types and high \pbest.

% Show the fraction of galaxies in each category as a function of p_features and p_odd?

>>>>

One of the major difficulties in studying the morphologies of galaxies in large samples lies in the system of measurement. Visual classification by experts has been used for many years \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}. These methods have advantages in using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration. Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{con03,lot04,sca07,bam08,fre13}, scale well to arbitrary sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts. The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images. With $>2\times10^5$~classifiers, this allows for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible. While the crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in Galaxy Zoo: Hubble. The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope which were used to create color gradients in the composite images for COSMOS.\label{fig:filtercurves}}
\end{figure*}

@@

Since the majority of the data in Legacy surveys described in \S\ref{ssec:legacy_surveys} had images in only 1 or 2~bands available when GZH was launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo was not possible. For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band is mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two. Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}. Note that the 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).

@@

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/specz_comparison.pdf}
\caption{Spectroscopic redshifts from the ACS-GC, 3DHST, and MUSYC catalogs. The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel. Within this range there is over 98\% agreement in redshifts between all three catalogs.}
\label{fig:speczs}
\end{figure*}

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
\caption{Flowchart of the questions presented to GZH users, labeled with the corresponding Task numbers. Tasks in the decision tree are color-coded by tier level: Gray-colored Tasks are 1st tier questions which are asked of all users. Tasks colored green, blue, purple, and pink (respectively) are one, two, three, or four steps below branching points in the decision tree.}
\label{fig:decisiontree}
\end{figure*}

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/zeta_examples.pdf}
\caption{Behavior of the normalized, weighted vote fractions of features visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the artifical \ferengi{} images. Galaxies are a random selection of images with $e=0$ and at least three detectable images in redshift bins of $z\ge0.3$. The measured vote fractions (red points) are fit with an exponential function (Equation~\ref{eqn:fzeta}); the best-fit parameters are given above each plot. Error bars are Poissonian, assuming a median of 40~votes per galaxy.}
\label{fig:zeta_examples}
\end{figure*}

@@

\begin{figure}
\center
\includegraphics[width=0.50\textwidth]{figures/zeta_mu.pdf}
\caption{All fits for the vote fraction dropoff parameter $\zeta$ for $f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface brightness. This includes only the 37~galaxies with a reasonably bounded range on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit the function.}
\label{fig:zeta_mu}
\end{figure}

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), uncorrectable (green), and NEI (pink) galaxies in the full GZH sample. The uncorrectable galaxies tend towards higher redshift, slightly lower in surface brightness, and lower values of $p_{features}$ than the correctable galaxies. The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
\label{fig:z_mu_p}
\end{figure*}

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), uncorrectable (middle), and NEI (right) galaxies in the GZH sample.}
\label{fig:debiased_corrections}
\end{figure*}

@@

\subsection{Comparison to other catalogs}\ref{ssec:comparisons}

@@
